INTELLIGENT SYSTEMS

### 2021-04-17 papers/paper_8.tex
finish paper8

\subsubsection{Template-Searching-Background Loss}
Several positive $X^+_i$, negative $X^-_i$ and background $B_{i-1,j}$ patches can be 
generated in an image. Patches are considered positive if they have a small 
cosine distance with the target template $T$, on the contrary, patches will be 
considered negative if they are closer to the background patches within the 
search region $S_i$. The loss function to be minimized is the following:
\begin{equation}
    L(T,\{X_{i,k}\}^N_{k=1}, \{B_{i-1}\}^M_{j=1}) = \sum_{k=1}^NL(T,X_{i,k}, \{B_{i-1,j}\}^M_{j=1})
\end{equation}
Where $T$ is the target template, $X_{i,k}$ is the $k-th$ candidate patch $X$ of frame 
$i$, $M$ is the number of background patches and $N$ is the number of candidate 
patches $X_{i,k}$.

@@

>>>>

\subsubsection{Template-Searching-Background Loss}
Several positive $X^+_i$, negative $X^-_i$ and background $B_{i-1,j}$ patches can be 
generated in an image. Patches are considered positive if they have a small 
cosine distance with the target template $T$, on the contrary, patches will be 
considered negative if they are closer to the background patches within the 
search region $S_i$. The loss-function calculation encourages the distance 
between a positive patch and the background patches to be greater than that 
between the positive patch and the target model.
\begin{equation}
    L(T,\{X_{i,k}\}^N_{k=1}, \{B_{i-1}\}^M_{j=1}) = log(1+e^{l_id_i})
\end{equation}
Where $T$ is the target template, $X_{i,k}$ is the $k-th$ candidate patch $X$ of frame 
$i$, $M$ is the number of background patches and $N$ is the number of candidate 
patches $X_{i,k}$. $d(\cdot)$ is the distance function:
\begin{equation}\label{distanceFunc}
    d_i=\sum^M_{j=1} D(T, X_i) - D(X_i, B_{i-1,j})
\end{equation}
where $D$ is the cosine distance that describe the distance of two image patches 
$X_1$ and $X_2$ and $l_i \in \{+1,-1\}$ is the ground truth label of $X_i$. Since the 
loss function must be calculated for each patch, the shortest distance will 
be chosen based on the values returned by the calculation of the following 
loss-function (\ref{FinalLoss}).
\begin{equation}\label{FinalLoss}
    L(T,\{X_{i,k}\}^N_{k=1}, \{B_{i-1}\}^M_{j=1}) = \sum_{k=1}^NL(T,X_{i,k}, \{B_{i-1,j}\}^M_{j=1})
\end{equation}

@@

\subsubsection{Result and Analysis}
\begin{enumerate}
    \item \emph{Comparison with Recent Real-Time Trackers}: the performance of each tracker, including the one proposed, is shown below. For the OTB dataset, several metrics are used to evaluate its tracking quality. Among these metrics we have those of AUC and precision, while for the VOT dataset the metrics specified above are used (Fig.\ref{fig:PerfComp}).
    \begin{figure}[h!]
        \centering
        \includegraphics[width = \linewidth]{images/paper8/metrics.png}
        \centering
        \caption{Performance comparison with Recent Real-Time Trackers}
        \label{fig:PerfComp}
    \end{figure}
    \item \emph{Attribute-Based Evaluation}: the presence of distracting elements leads 
    many methods to fail to track them. In figure \ref{fig:AUCScore} it is possible to see the 
    comparison, in terms of AUC score, reached by different methods on 
    the OTB-2013 dataset, when these elements are present. The values 
    in blue are the highest and are obtained from the best method, while 
    those in red are placed in second position.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = \linewidth]{images/paper8/AUC.png}
        \centering
        \caption{AUC score on OTB-2013 dataset.}
        \label{fig:AUCScore}
    \end{figure}
    \item \emph{Qualitative Evaluation}: The use of the Template-Searching-Background (TSB), allows you to use the background patches to train the model (Fig.\ref{fig:TSBMin}). This method helps to minimize the relative distance $d(\cdot)$ (\ref{distanceFunc}) which translated into other words means bringing the target template closer to the $X_i^+$ samples and at the same time moving the background distractors $B_i$ away from the positive sample. This method allows for better performance than existing state-of-the-art models. A visual example of comparison of the trackers made by the different methods, including the one proposed, is visible in figure \ref{fig:qualitativeTracking}.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = \linewidth]{images/paper8/TSB.png}
        \centering
        \caption{Template-Searching-Background to minimizes the relative distance.}
        \label{fig:TSBMin}
    \end{figure}
    \begin{figure}[h!]
        \centering
        \includegraphics[width = \linewidth]{images/paper8/qualitative.png}
        \centering
        \caption{Qualitative reuslt of seven trackers. The bounding box with an orange dotted line shows the ground-truth localization of the target object.}
        \label{fig:qualitativeTracking}
    \end{figure}
\end{enumerate}

\subsection{CONCLUSION}
The proposed framework, from the results obtained in the benchmarks, seems 
to be the best. The achievement of these results were possible thanks to the 
integration of a verification and detecting method. The use of the TSB 
method was fundamental, which, by reducing the relative distance between 
the various patches, allowed for good model learning.
